\documentclass{beamer}
\usepackage{etex}
\usepackage{url}
\usepackage{semantic}
\usepackage{pgfpages}
\usepackage{multicol}\columnseprule 0.4pt
\usepackage{subfigure}
\usepackage{tikz,tikz-qtree}
\usepackage{verbatim,fancyvrb}
\usepackage{mathtools,mathrsfs,amsmath,amsthm,amsfonts}

%% Symbolic, relative link to thesis graphics.
\graphicspath{ {./pics/}{./extra/} }

%% Optional: Turn on Notes Pages:
\setbeameroption{show notes on second screen}

%% Beamer Theme Options
\usetheme{Rochester} % Because RIT.
\usecolortheme[named=black]{structure} % Default

%% Document Information:
\title{Process Cooperativity as a Feedback Metric\\
        in Concurrent Message-Passing Languages}
\author{Alexander Dean}
\institute{
    Rochester Institute of Technology\\
    Golisano College of Computer and Information Sciences
}
\date{August 12, 2014} % Scheduled Defense Date
\subject{Thesis Defense}

%% Document Table-Of-Contents, and pacing slides.
\AtBeginSection[]
{
    \begin{frame}
        \frametitle{\insertsection}
        \begin{multicols*}{2}
            \tableofcontents[sectionstyle=show/hide,
                             subsectionstyle=show/show/hide]
        \end{multicols*}
        \note{Introduce the new section:\hfill
              \tableofcontents[sectionstyle=show/hide,
                               subsectionstyle=show/show/hide]}
    \end{frame}
}

%% Slides have titles based on their section and subsection.
\newenvironment{slide}
    {\begin{frame}[environment=slide,fragile]
            \frametitle{\insertsection: \insertsubsection}
    }
    {\end{frame}}

%% Itemized Notes:
\newcommand{\inote}[1]{\note{\begin{itemize} #1 \end{itemize}}}

%% Abbreviations:
\newcommand{\etc} {\emph{etc.\/}}
\newcommand{\etal}{\emph{et~al.\/}}
\newcommand{\eg}  {\emph{e.g.\/}}
\newcommand{\ie}  {\emph{i.e.\/}}

\begin{document}

% TITLE PAGE:
\frame{\titlepage
    \inote{
        \item Thank Fluet, Heliotis, and Raj.
        \item Dedicate to parents, who are unable to be present.
    }
}

% ToC PAGE:
\begin{frame}
    \frametitle{Process Cooperativity as a Feedback Metric}
    \framesubtitle{in Concurrent Message-Passing Languages}
    \begin{multicols*}{2}
        \tableofcontents
    \end{multicols*}
    \inote{
        \item Mouthful of a title, so I'll break it up:
        \begin{enumerate}{\scriptsize
            \item Runtime scheduling, to give some grounding in the area of study.
            \item Cooperativity, what it is and motivation to use it.
            \item Message Passing, because, as it turns out, it's a nice 
                abstraction for our purpose of capturing cooperativity.
            }
        \end{enumerate}
        \item The core of the work revolves around the toolkit I built.
            \begin{itemize}{\scriptsize
                \item A language/compiler/runtime/testing-framework
                \item But also a {\sl Simulator} which has a plug-and-play 
                    scheduler API. It let me test schedulers on a common test 
                    bed.
                }
            \end{itemize}
        \item Next, go over the list of schedulers \& feedback mechanisms.
        \item Results, Conclusions, \& Future Work.
    }
\end{frame}

% INCLUDE EACH SECTION:
\input{sections/1background}
\input{sections/2erlam}
\input{sections/3schedulers}
\input{sections/4results}
\input{sections/5conclusions}

% Questions and Thank you!
\section*{Questions}
\begin{frame}
    \begin{center}
        {\Huge Questions/Comments?}
    \end{center}

    \uncover<2->{
        \begin{center}
            Thank You!
        \end{center}
    }
\end{frame}

% Bibliography and Links Sections:
%\input{sections/999bibliography}
\input{sections/9999links}

\end{document}
