\section{Conclusions \& Future Work}

\subsection{ErLam Toolkit}

\begin{slide}
    \begin{itemize}
        \item Test Primitives were nicely composable process behaviours.
            \begin{itemize}
                \item More research into generating behaviours.
                \item More compositions: PTree with Rings.
            \end{itemize}

        \item Log generation, lots of overhead, but good observations.
    \end{itemize}

    \inote{
        \item Overall pleased with simulator and achieved its goal.
        \item Future Work: 
            \begin{itemize}
                \item Generate more test primitives, a good library of them 
                        would be nice.
                \item Compose them easier and more frequently. Perhaps 
                    generating work groups as PRing might have made a better 
                    comparison than Interactivity.
 
                \item Clean up log generation (reduce overhead).
                \item Process evaluation uses alpha-reduction 
                      (can be sped up substantially).
                \item Make schedulers more adjustable (different
                        spawn/yields/etc).
                \item More Channel implementations
            \end{itemize}
    }
\end{slide}

\subsection{Cooperative Schedulers}

\begin{slide}
    \begin{itemize}
        \item {\bf Longevity Batching:}
            \begin{itemize}
                \item Would benefit from heuristic based Quantum selection.
                \item As it stands, limited gain from longevity recognition.
                \item[] ~
            \end{itemize} 
        \item {\bf Channel Pinning:}
            \begin{itemize}
                \item Promising saturation and work-stealing mechanic.
                \item[] ~
            \end{itemize}
        \item {\bf Bipartite-Graph Aided Sorting:} 
            \begin{itemize}
                \item Supprising results on MapReduce style applications.
                \item Worth studying Blocking-Channels further for gains from 
                    sorting.
            \end{itemize}
    \end{itemize}

    \inote{
        \item SS: Would benefit from merging with Channel Pinning. Increase 
            likelihood that sorting puts channel partners close.
    
        \item LBB + CP might be interesting as channels could own batches.

        \item Overhead of Sorting? If implemented in a practicle language,
            would it be worth it? Seems counter-intuitive but promising as is.
    }
\end{slide}

\subsection{Cooperativity as a Metric}

\begin{slide}

    \begin{itemize}
        \item Possible to recognize and benefit from.
        \item The three example mechanics are promising and can be extended for
                practicle modern languages, despite simplistic simulation language.
        \item More to explore:
            \begin{itemize}
                \item Alternate Message-Passing Types (Asymmetric?)
                \item \ldots
            \end{itemize}
    \end{itemize}

    \inote{
        \item Promising scheduling mechanics
        \item More research is necessary in the message-passing implementation
                for it to be practical in common languages.
        \item (Asymmetric/Directionality would be first on the list)
    }
\end{slide}


