\chapter{Results and Discussion}
\index{Results and Discussion@\emph{Results and Discussion}}%
\label{chap:results}

\section{Evaluation}\label{sec:results-evaluation}

\todo[inline]{Evaluation of each scheduler will consist of complete testing:\\
- Run $PTree_N$ for $1 \leq N \leq P+1$ where $P$ is number of processors.\\
- Run $PRing_N$ for $N \in \{ 1, P, B-1, B, 2*B \}$ where $B$ is max batch size where applicable.\\
- Run $ClusterComm_{(N,M)}$ for $N \in \{ 2, 4, ..., P, B, 2*B \}$ and $ 1 \leq M \leq \lfloor N / 2 \rfloor$ \\
- Run $ChugMachine_N$ for $1 \leq N \leq P+2$  \\
- Run $JumpShip_{(W,H)}$ for $2 \leq W \leq P+1$ and $1 \leq H \leq 3$ 
}

\todo[inline]{Composing simulations may lead to interesting results though. 
I would like to test, at least: \\

- $UserInput$ and $ChugMachine$ to examine Interactivity.\\
- $PTree$ and $ChugMachine$ or $ClusterComm$ to have both structured subcomponents, and otherwise.
}

\subsection{Classical Schedulers}\label{sec:results-evaluation-classical}

\todo[inline]{ There are 5 schedulers, STRR, STDQ, MTRRGQ, MTRRWS-SQ, MTRRWS-IS which 
need to be evaluated. However, I wont know what's interesting until after all tests have
been run.}

\subsection{Cooperativity Feedback Schedulers}\label{sec:results-evaluation-feedback}

\todo[inline]{ There are 3 schedulers, Longevity-Batcher, Channel-Pinner, Graph Shuffling.
I will primarily be looking at:\\

- How does Longevity Batcher degrade? Does it turn into MTRRWS?\\
- How quickly and thoroughly can Channel-Pinner saturate the cores with work?\\
- How does Graph Shuffling handle large and small process queues?
}


\section{Comparisons}\label{sec:results-comparisons}

\todo[inline]{ Including the above, I will want to compare:\\
- MTRRWS-SQ and MTRRWS-IS \\
- STRR and MTRRGQ \\
- Long-Batcher and Channel-Pinner in terms of work-stealing \\
- All feedback schedulers in terms of: execution time (tick count), saturation, evenness of work-load.
}

\section{A Comment on Swap Channels}\label{sec:results-swap-channels}

\todo[inline]{Namely, we're using an odd channel implementation that most 
languages do not choose. How did that work out for us?\\

- In implementing example applications, \\
- In terms of applicability of findings to other message-passing implementations,\\
- etc.
}
